---
title: "jap demo"
author: "Giovanni Laudanno"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{jap demo}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

First, specify basic info

```{r setup, include = FALSE}
account <- "p274829"
project_name <- "mbd"
cluster_folder <- "home"
projects_folder_name <- "Projects"
drive <- TRUE # we want to use google drive
```

Then open a session. We are gonna use this session every time we want to execute tasks on the cluster

```{r}
library(jap)
session <- jap::open_session(account = account)
```

Then we setup the entire folder structure on three different places: local, peregrine and google drive

```{r}
jap::create_folder_structure(
  project_name = project_name,
  projects_folder_name = projects_folder_name,
  cluster_folder = cluster_folder,
  drive = drive,
  account = account,
  session = session
)
```

We can check the structure on the remote folder and on the drive folder

```{r}
jap::remote_list.files(
  dir = projects_folder_name,
  cluster_folder = cluster_folder,
  account = account,
  session = session
)
jap::drive_list.files(
  dir = projects_folder_name
)
```

We can now install the package we need from Github

```{r}
jap::remote_install.packages(
  github_name = "Giappo",
  package_name = project_name,
  account = account,
  session = session
)
```

We can even install any package from CRAN. To do so it suffices to not specify the 'github_name' argument

```{r}
jap::remote_install.packages(
  package_name = "DDD",
  account = account,
  session = session
)
```
