---
title: "pocket demo"
author: "Giovanni Laudanno"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{pocket demo}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

First, specify basic info

```{r setup, include = FALSE}
account <- jap::your_account()
projects_folder_name <- "Projects"
drive <- TRUE # we want to use google drive
library(jap, quietly = TRUE)
```

Now we can set it up to work using the "sls_main" function from the "sls" package taken from the Github repo named "Giappo":

```{r}
github_name <- "Giappo"
project_name <- "sls"
library(project_name, character.only = TRUE)
function_name <- "sls_main"
max_sims <- 3
params_grid <- expand.grid(
  lambda_m = c(0.3, 0.6),
  mu_m = c(0.1, 0.2),
  lambda_s = 0.8,
  mu_s = 0.1,
  crown_age = 8,
  shift_time = 5,
  cond = 3,
  seed = 1:max_sims
)
loglik_functions <- sls::sls_logliks_experiment()
verbose <- TRUE
project_folder <- file.path("", "home", account, projects_folder_name, project_name)

params <- vector("list", nrow(params_grid))
for (i in 1:nrow(params_grid)) {
  params[[i]]$sim_pars <- unlist(params_grid[i , sls::get_param_names()])
  params[[i]]$crown_age <- params_grid[i , "crown_age"]
  params[[i]]$shift_time <- params_grid[i , "shift_time"]
  params[[i]]$cond <- params_grid[i , "cond"]
  params[[i]]$seed <- params_grid[i , "seed"]
  params[[i]]$loglik_functions <- loglik_functions
  params[[i]]$verbose <- verbose
  params[[i]]$project_folder <- project_folder
}
```

Now we just need to call the function "pocket_experiment" to run everything

```{r}
jap::pocket_experiment(
  github_name = github_name,
  project_name = project_name,
  function_name = function_name,
  params = params,
  account = account,
  projects_folder_name = projects_folder_name,
  drive = FALSE
)
```

We can also try to run other projects. For example let's try with "mbd"

```{r}
github_name <- "Giappo"
project_name <- "mbd"
library(project_name, character.only = TRUE)
function_name <- "mbd_main"
max_sims <- 2
params_grid <- expand.grid(
  lambda = c(0.2, 0.4),
  mu = c(0.05, 0.1),
  nu = c(0.5, 1),
  q = 0.1,
  age = 8,
  cond = 1,
  seed = 1:max_sims
)
loglik_functions <- mbd::mbd_experiment_logliks()
verbose <- TRUE
project_folder <- file.path("", "home", account, projects_folder_name, project_name)

params <- vector("list", nrow(params_grid))
for (i in 1:nrow(params_grid)) {
  params[[i]]$sim_pars <- unlist(params_grid[i , mbd::get_param_names()])
  params[[i]]$age <- params_grid[i , "age"]
  params[[i]]$cond <- params_grid[i , "cond"]
  params[[i]]$seed <- params_grid[i , "seed"]
  params[[i]]$loglik_functions <- loglik_functions
  params[[i]]$verbose <- verbose
  params[[i]]$project_folder <- project_folder
}
```

Again, we just need to run "pocket_experiment" to make everything run

```{r}
jap::pocket_experiment(
  github_name = github_name,
  project_name = project_name,
  function_name = function_name,
  params = params,
  account = account,
  projects_folder_name = projects_folder_name, 
  drive = drive
)
```

Let's try with "DAISIErobustness"

```{r}
drive <- TRUE
account <- jap::your_account()
github_name <- "Neves-P"
project_name <- "DAISIErobustness"

# Project Settings
jap::install_package(package_name = project_name, github_name = github_name)
library(project_name, character.only = TRUE)
function_name <- "run_robustness"

# Create params for the experiment
param_space <- DAISIErobustness::load_param_space(
  param_space_name = "oceanic_ontogeny"
)
params <- vector("list", nrow(param_space))
for (i in 1:nrow(param_space)) {
  params[[i]] <- list(
    param_space_name = "oceanic_ontogeny",
    param_set = i,
    replicates = 2,
    save_output = TRUE
  )
}

```

Again, we just need to run "pocket_experiment" to make everything run

```{r}
jap::pocket_experiment(
  github_name = github_name,
  project_name = project_name,
  function_name = function_name,
  params = params,
  account = account,
  projects_folder_name = projects_folder_name, 
  drive = FALSE
)
```

We can check that everything is running

```{r}
jap::check_jobs(account = account)
```

Or we can check if our results are stored on google drive

```{r}
jap::drive_list.files(dir = "sls/results")
jap::drive_list.files(dir = "mbd/results")
```
