---
title: "jap demo"
author: "Giovanni Laudanno"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{jap demo}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

First, specify basic info

```{r setup, eval = FALSE}
account <- jap::your_account()
project_name <- "mbd"
projects_folder_name <- "Projects"
drive <- TRUE # we want to use google drive
```

A note on using the `drive` option. The set of tools of that feature use the
tidyverse package `googledrive`, which requires a short set-up. First call
`googledrive::drive_auth()`, this will open a pop-up window asking you to
sign-in your Google account, and grant permission to `googledrive` to access and
edit your Drive folders.
There is a common issues with the Google API, reported [here](https://github.com/tidyverse/googledrive/issues/279) for example. There
is a fix to this on the latest implementation on GitHub, but not yet on CRAN (as
of 27/04/2020). So we recommend:
```{r install_googledrive, eval=FALSE}
remotes::install_github("tidyverse/googledrive")
```

Then open a session. We are gonna use this session every time we want to execute tasks on the cluster

```{r eval=FALSE}
library(jap)
session <- jap::open_session(account = account)
```

Then we setup the entire folder structure on three different places: local, peregrine and google drive

```{r eval=FALSE}
jap::create_folder_structure(
  project_name = project_name,
  projects_folder_name = projects_folder_name,
  drive = drive,
  account = account,
  session = session
)
```

We can check the structure on the remote folder and on the drive folder

```{r eval=FALSE}
jap::remote_list_files(
  dir = projects_folder_name,
  account = account,
  session = session
)
jap::drive_list_files(
  dir = projects_folder_name
)
```

We can now install the package we need from Github

```{r eval=FALSE}
jap::remote_install_packages(
  github_name = "Giappo",
  package_name = project_name,
  account = account,
  session = session
)
```

We can even install any package from CRAN. To do so it suffices to not specify the 'github_name' argument

```{r eval=FALSE}
jap::remote_install_packages(
  package_name = "ape",
  account = account,
  session = session
)
```

Or we can run a function

```{r eval=FALSE}
cluster_folder <- "data"
jap::run_on_cluster(
  package_name = "ape",
  function_name = "rtree",
  fun_arguments = "n = 10",
  cluster_folder = cluster_folder
)
```

```{r eval=FALSE}
jap::remote_list.files(dir = "jap_scripts", cluster_folder = cluster_folder)
```
